A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

Upscaling methods replace discrete geological and fluid properties of detailed (high-resolution) domains with coarse descriptions (low-resolution) of these properties \cite{Vereecken_2007}. Upscaling of heterogeneous properties has attracted the interest of several porous media flow communities (\eg oil and gas, CCS and waste management) worldwide for over $7$ decades.

Those interested in large-scale reservoirs or ground water generally take a two-stage geostatistical approach. In the first stage, information from seismic data, well data and analogous outcrops is used to model the large scale heterogeneities associated with facies. In the second stage, statistical models such as continuous multi-variate Gaussian field is used to model the rock properties of the facies \cite{Ewing_1997}. In addition to seismic and well data used in the previous stage, core data can be used as a sources of information for the statistical properties used to determine the random field in this stage.

>>>>

Upscaling methods replace discrete geological and fluid properties of detailed (high-resolution) domains with coarse descriptions (low-resolution) of these properties \cite{Vereecken_2007}. Upscaling of heterogeneous properties has attracted the interest of several porous media flow communities (\eg oil and gas, CCS and waste management) worldwide for over $7$ decades. Those interested in large-scale reservoirs or groundwater generally take a two-stage geo-statistical approach.

In the first stage, information from seismic data, well data and analogous outcrops is used to model the large-scale heterogeneities associated with facies. In the second stage, statistical models such as continuous multi-variate Gaussian field is used to model rock properties of the facies \cite{Ewing_1997}. In addition to seismic and well data used in the previous stage, core data can be used as a source of information for the statistical properties used to determine random fields in this stage.
